%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Machine Learning Engineer} % Affiliation/role
{Hackathon "Цифровой прорыв. Сезон: Искусственный интеллект (ПФО)"} % Organization/group
{Perm, Russia} % Location
{October 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {The main objective was to find a solution to the problems of detecting and tracking solid waste items in the multispectral images.}
    \item {The YOLOv8 model was used to solve the detection problem. } 
    \item {My task was to manage the team within the machine learning and data preprocessing tasks. }
    \item {I researched current models and methods for solving detection and tracking problems. }
    \item {I analyzed the data as it was fed in a non-standard format due to channels other than RGB. }
    \item {I dealt with augmentations of the input data. }
    \item {I modified the YOLOv8 model from the Ultralitycs library to allow it to accept eleven-channeled images. }
    \item {After expert evaluation our solution was ranked second. }
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Backend Engineer} % Affiliation/role
{Hackathon VTB MoreTECH 5.0} % Organization/group
{Online} % Location
{October 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {The task was to display VTB Bank branches in a user-friendly interface to make it easier to find the most suitable branch. }
    \item {Our team used Flutter to write the mobile app and FastAPI to write the backend part. } 
    \item {To find the best branch, our team decided to use two metrics: branch occupancy and the time it takes for a customer to get to the branch by the chosen mode of transportation. }
    \item {To measure branch occupancy, we suggested using surveillance camera images every twenty minutes, to count the number of people and keep statistics in case of system failure.}
    \item {In the course of my work, I integrated a microservice that tracks the occupancy of bank branches. For integration I used RabbitMQ. }
    \item {Our team made it to the finals (top 10), but did not win any places. }
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Machine Learning Engineer} % Affiliation/role
{Hackathon "Цифровой прорыв. Сезон: Искусственный интеллект (Международный)"} % Organization/group
{Online} % Location
{November 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {The task of the hackathon was to identify infrastructure objects in satellite images. }
    \item {I managed a team within the machine learning and data preprocessing tasks. }
    \item {During the hackathon, I studied the literature to test out-of-the-box models for our task, unfortunately for the methods proposed in the research, we lacked time and computational resources, so it was decided to fine-tune a pre-trained model. }
    \item {Our solution was a trained Unet model. } 
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Machine Learning Engineer} % Affiliation/role
{Hackathon IT Inno Hack} % Organization/group
{Online} % Location
{September 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {We were given the task of merging records. }
    \item {The data were three databases with information about people, it was necessary to merge the records related to the same person. }
    \item {The data were corrupted: some records had missing fields, others had typos, and sometimes words could be duplicated. }
    \item {An important problem was that 11 million records had to be analyzed in 20 minutes. }
    \item {I researched the literature related to our topic and the methods used to solve the Record Linkage problem. } 
    \item {The solution to the problem was to use the Expectation-Maximization algorithm with Levenshtein distance. }
    \item {After evaluating the solutions, our team came in fourth place with a minimal gap from the winners. }
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Machine Learning Engineer} % Affiliation/role
{Hackathon "Цифровой прорыв. Сезон: Искусственный интеллект (ПФО)"} % Organization/group
{Nizhniy Novgorod, Russia} % Location
{October 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {The task was to detect flooded regions and infrastructure on multispectral satellite images. from satellites. }
    \item {In addition, one of the metrics was to count the number of houses that were flooded. }
    \item {I was engaged in reviewing research relevant to our task. } 
    \item {During the solution, I implemented an algorithm that utilizes the surface reflectance features through a modified co-occurrence matrix for color images, as well as an algorithm to train a generative-adversarial network. }
    \item {As a solution, we provided a generative-adversarial network with the Unet model as the generator. } 
    \item {As a result, our team took the seventh place.}
  \end{cvitems}
}
\end{cventries}
